sensiAnPaper1All

### 2015-07-01 sensiAnPaper1All.Rmd
sensitivity analysis improvements

  nScenarios <- 100
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

@@

### here I want a file with the inputs (just one value for exposure)
### with extra columns for seq
```{r}
treeInput <- rbind( listOutMix$input, resistBetterMix1Seq )

@@

  #return(listOut)

}

>>>>

  #default setting of the random seed in sensiAnPaperPart() should make the input files mostly the same with exception of exposure

  nScenarios <- 100
  #nScenarios <- 10
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

  #in 100 runs for all 3 critical points sequential was better than mix1 all the time

@@

### bind results onto input file
```{r}

  treeInput <- listOutMix$input

  #input files in listOutMix, listOutIn1 & listOutI2 are the same if the runs are done with default randomSeed 
  #except that exposure will be in a.f_AB, a.f_A0 and a.f_B0 respectively (& a.m* too)
  #I could just rename one to exposure
  rownames(treeInput)[rownames(treeInput)=="a.f_AB"] <- "exposure"

  #hardcode which variables to include in the tree analysis here
  #to keep it simple and transparent
  treePredictors <- c('P_1','P_2','exposure','phi.SS1_A0','phi.SS2_0B','h.RS1_A0','h.RS2_0B','s.RR1_A0','s.RR2_0B')
  treeInput <- treeInput[ treePredictors, ]

  treeInput <- rbind( treeInput, resistBetterMix1Seq )
  #todo add other results rows here

@@

### do tree analysis
```{r}
  require(rpart)

  #transpose
  treeInput <- t(treeInput)
  #convert to a dataframe
  treeInput <- data.frame(treeInput)

  treePredictorString <- paste(treePredictors, collapse="+")
  treeResponse <- 'betterMix1Seq_cP0.5'

  #at 0.5 level
  tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
  #getting error number of rows of matrices must match (see arg 2)
  #may be becuase all vals are 0 ??
  #yes when I added some 1s it worked OK
  #treeInput$betterMix1Seq_cP0.5[1:5] <- 1

  #using as.formula
  #tree <- rpart::rpart(as.formula(paste("res ~",argString)), data = inputAndResults, method = 'class')  
  #hardcoded args
  #tree <- rpart(res ~ h.RS1_A0 + h.RS2_0B, data = inputAndResults, method = 'class')
  #tree <- rpart(betterMix1Seq_cP0.5 ~ h.RS1_A0 + h.RS2_0B, data = treeInput, method = 'class')

  plot(tree) #plots tree
  text(tree) #labels tree

    #pruning tree
    #   treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])
    #   plot(treePruned) #plots tree
    #   text(treePruned) #labels tree
